---
title: "Registered Replication Report: Hayakawa & Keysar (2017)"
shorttitle: "Using a foreign language reduces mental imagery"
author: "Peter Crowe, Eric Hrybinski, Pauline Schreich"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
output: word_document
---
```{r setup, include=FALSE, echo = FALSE, message = FALSE}

knitr::opts_chunk$set(echo=TRUE, 

                      warning=FALSE,

                      message=FALSE, 

                      collapse = TRUE,

                      cache = TRUE,

                      dev.args = list(bg = 'transparent'), 

                      fig.align='center', 

                      fig.height = 3, 

                      fig.widht=4)

library(rmdformats)

library(tidyverse)

library(brms)

library(ggplot2)

library(knitr)

options(mc.cores = parallel::detectCores())

```

```{r, echo = FALSE}

data <- read_csv("1-1.csv")

```

# Abstract
abstract, theoretical background, research question  
Why is this interesting?

# Methods

## Design
1 x 2 between subject design  
dependant variable = vividness (1 - 7)  
independent variable = cue (Bett's Questionnaire)

### Participants
Participants will be German-speaking (possibly non-native) adults with some proficiency in English as a foreing language  
Participants will be recruited among Cognitive Science Bachelor students of the university of Osnabrück during the summer semester 2019.   Recruitment happens via e-mail invitation providing a link to the online experiment  
We will collect data from as many participants as we can recruit over a period of two weeks  
sample size = `r data$submission_id %>% unique %>% length`

## Materials
Bett's Questionnaire (shortened as we got rid of all of the words deemed to similar in German and English)

## Procedure
-Instructions: Participants are shown written instructions about the tasks to come.  
-Proficiency test: Participants of the FL group are tasked to translate 5 -English words into German  
-Practice run: Subjects tasked to assess 5 examples to get comfortable with the process  
-Main phase: Subjects are presented with a sensory cue. They are shown the modality of the cue as well as the cues description. They are presented with a dropdown menu in which to choose a written out description of the vividness.  


# Analysis

## Exclusion criteria
failed translation test  
targeted NL not actually the NL of subject  
targeted FL actually the dominant language of subject, crossed "do not understand"  

## Preregistered analysis plan
analysis plan
```{r}
data
```

# Results
results